---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# flaky

<!-- badges: start -->
<!-- badges: end -->

The goal of flaky is to provide a dplyr backend and various helpers for using [Snowflake](https://www.snowflake.com/) with R. You may know about Snowflake's similar package [dplyr.snowflakedb](https://github.com/snowflakedb/dplyr-snowflakedb), but that requires rJava, a notriously difficult package to use. Flaky is meant to be use with Snowflake's ODBC drivers which work well within the Rstudio environment, once you [get them installed](https://www.ndiquattro.me/blog/2020/02/snowflake-r-and-dbplyr/).

## Installation

Currently, flaky is only available through [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("ndiquattro/flaky")
```
## Example

```{r example, eval=FALSE}
library(dplyr)
library(flaky)

con <- flaky_connect("snowflake_dsn")

con %>% 
  tbl(dbplyr::in_schema("schema", "table")) %>% 
  filter(coolness > 10, str_detect(rpackages, "flak")) %>% 
  collect()
```
